%-------------------------------------------------------------------------------
%   SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Personal Projects}


%-------------------------------------------------------------------------------
%   CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Deep Learning, \href{https://github.com/willard-yuan/CNN-for-Image-Retrieval}{\color{blue}{Code}}} % Job title
    {CNN for Image Retrieval} % Organization
    {} % Location
    {Apr. 2015 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched content-based image retrieval using VGG convolutional neural network.}
        \item {Implemented prototype that users can obtain semantic similarity image relevant to a query on web site.}
        \item {Optimized the query response speed to make sure it responds to the user’s query in a timely manner.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Approximate Nearest Neighbor Research, \href{https://github.com/willard-yuan/hashing-baseline-for-image-retrieval}{\color{blue}{Code}}} % Job title
    {Hashing Baseline for Image Retrieval} % Organization
    {} % Location
    {Feb. 2013 - Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed a framework to validate the performace of various hashing methods with different evaluations.}
        \item {Implemented some hashing methods, and proposed new hashing method for image retrieval.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
  \cventry
    {Object Retrieval} % Job title
    {DuplicateSearch} % Organization
    {} % Location
    {Jun. 2015 - Mar. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented the BoW, VLAD, and Fisher Vector encoding methods using VLFeat, and conducted object retrieval experiments on a 100,000 clothes and shoes image dateset.}
        \item {Built multithreads using openMP to speed up feature extraction and clustering.}
        \item {Improved the mean average precision using the RANSAC reranking algorithm.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Face Image Retrieval System, \href{https://github.com/willard-yuan/SeetaFaceLib}{\color{blue}{Code}}} % Job title
    {SeetaFaceLib} % Organization
    {} % Location
    {Sep. 2016 - Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a face image retrieval system using CNN method based on SeetaFaceEngine.}
        \item {Optimized the query respond speed using Local Sensitive Hashing methood.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
