%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Algorithm Engineer} % Job title
    {Kuaishou} % Organization
    {Beijing, China} % Location
    {Dec. 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Focused on Video Copy Detection and developed a video similarity reranking and video copy validation method.}
        \item {Designed and developed two logo recognition algorithms based on OCR and Faster RCNN. Updated old logo recognition based on local feature. The precision is 99.6\% and the logo algorithms recall 70,000 logo videos if the number of uploaded videos is 6400,000.}
        \item {Researched and developed Content-Based Image Retrieval system based on fusion CNN feature and hand-craft feature. The mean average precision achieved 80\% on Oxford Building dataset.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Algorithm Developer} % Job title
    {Meituan} % Organization
    {Beijing, China} % Location
    {Jul. 2016 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and Developed anti-cheat strategies to fetch sellers who violate the rules of the meituan online takeaway platform.}
        \item {Analyzed data of the meituan takeaway business for risk control. Did report forms to monitor some important data.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Algorithm Engineer} % Job title
    {Etracker Team (Student's Start-up)} % Organization
    {Xi'an, China} % Location
    {Oct. 2015 - Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented eye-gaze detection algorithms to track pupil using C++, OpenCV and OpenMP.}
        \item {Implemented eye tracker calibration algorithms to map attention coordinates to screen coordinates, and developed pupil tracking desktop application using QT.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher for Content Based Image Retrieval (CBIR), Undergraduate Research} % Job title
    {OPTical IMagery Analysis and Learning Lab (Prof. Xuelong LI)} % Organization
    {Xi'an, China} % Location
    {Sep. 2013 - Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched large-scale content based image retrieval method including hashing based method and product quantion method.}
        \item {Proposed new hashing based methods for CBIR using sparse coding and matrix factorization.}
        \item {Built object detection system using HOG and SVM method for a 973 program.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
