%-------------------------------------------------------------------------------
%   SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Personal Projects}


%-------------------------------------------------------------------------------
%   CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Researcher for <Detecting video’s torrents using image similarity algorithms>} % Job title
    {Undergraduate Research, Computer Vision Lab(Prof. Bohyung Han)} % Organization
    {Pohang, S.Korea} % Location
    {Sep. 2012 - Feb. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched means of retrieving a corresponding video based on image contents using image similarity algorithm.}
        \item {Implemented prototype that users can obtain torrent magnet links of corresponding video relevant to an image on web site.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DuplicateSearch} % Job title
    {Software Maestro (funded by Korea Ministry of Knowledge and Economy)} % Organization
    {Seoul, S.Korea} % Location
    {Jul. 2012 - Jun. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Extracted SIFT feature descriptor to overcome brigthness variance, rotation variance, translation variance and scale variance.}
        \item {Quantized each extracted local feature into one of visual words, and then represent each image with a global feature by histogram of the visual words.}
        \item {Built multithreads by openMP to speed up feature extraction and the process of clustering.}
        \item {Improved the mean average precision (mAP) by reranking algorithm.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {PicSearch Web Application} % Job title
    {ShitOne Corp. (Start-up company)} % Organization
    {Seoul, S.Korea} % Location
    {Dec. 2011 - Feb. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Completed feature extraction offline and made dimensionality reduction.}
        \item {Deployed the prototype with the lightweight web development framework CherryPy.}
        \item {Optimized the code to make sure it respond to the user’s query (milliseconds) in a timely manner.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Hashing Baseline for Image Retrieval} % Job title
    {SAMSUNG Electronics} % Organization
    {S.Korea} % Location
    {Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented some hashing methods, note some hashing methods were found at the authors homepages, and inserted them to the framwork.}
        \item {Implemented some evaluations for validating the effectiveness of hashing methods, and made the evalua- tions complete.}
        \item {Designed and proposed new hashing methods for image retrieval based on the toolbox.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
