%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Algorithm Engineer} % Job title
    {Meituan} % Organization
    {Beijing, China} % Location
    {Dec. 2011 - Feb. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a proxy drive smartphone application which connects proxy driver and customer. Implemented overall Android application logic and wrote API server for community service, along with lead engineer who designed bidding protocol on raw socket and implemented API server for bidding.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer \& Security Researcher (Compulsory Military Service)} % Job title
    {ETRACKER Team (Student's Start-up)} % Organization
    {Xi'an, China} % Location
    {Oct. 2015 - Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a military cooperation system which is web based real time messenger in Scala on Lift.}
        \item {Improved functionality on military command and control system for incident response with Java Servlet.}
        \item {Lead engineer on agent-less backtracking system that can discover client device's fingerprint(including public and private IP) independently of the Proxy, VPN and NAT.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher for <Content Based Image Retrieval>} % Job title
    {Undergraduate Research, OPTical IMagery Analysis and Learning Lab(Prof. Xuelong LI)} % Organization
    {Pohang, S.Korea} % Location
    {Sep. 2013 - Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched means of retrieving a corresponding video based on image contents using image similarity algorithm.}
        \item {Implemented prototype that users can obtain torrent magnet links of corresponding video relevant to an image on web site.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
